Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-19 paper/sheaf_lics.tex
pass on intro

  Sheafification is a popular tool in topos theory which
  allows to extend the internal logic of a topos with new
  principles. One of its most famous applications is the possibility
  to transform a topos into a boolean topos using the
  dense topology, which corresponds in essence to Gödel's double
  negation translation.
  % 
  The same construction has not been developed in Martin-Löf type
  theory because of a mismatch between topos theory and type theory. This
  mismatched has been fixed recently by considering homotopy type
  theory, an extension of Martin-Löf type theory with new
  principles inspired by category theory and homotopy theory, and
  which corresponds closely to higher topoi.
  % 
  In this paper, we give a computer-checked construction of
  Lawvere-Tierney sheafification in homotopy type theory, which allows
  in particular to give a meaning to the (propositional) law of
  excluded middle inside homotopy type theory, being
  compatible with the full type-theoretic axiom of choice.

@@

Sheafification~\cite{maclanemoerdijk} is a very powerful geometric
construction that has been initially stated in topology and has
quickly been lifted to mathematical logic.
%
In the field of topos theory, it provides a way to construct new topoi
from already existing ones, allowing logical principles---that can not
be proven to be true or false in the old topos---to be valid (or
invalid) in the new topos.
%
The most common use of sheafification is the construction a boolean
topos, thus validating the classical principle of the law of excluded
middle (EM), from an intuitionistic topos using the dense topology. 
%
An other famous application has been developed by
Cohen~\cite{cohen1966} to prove that the continuum hypothesis is
independent of the usual axioms of Zermelo-Fr\ae nkel set theory, even
in presence of the axiom of choice (AC). The initial work of Cohen
uses forcing but can be rephrased in terms of
sheafification~\cite{maclanemoerdijk}.

@@

Unfortunately, all those works---although they provide very nice and
sophisticated theoretical results---do not share the generality and
simplicity of sheafification in topos theory and are not amenable to a
direct integration into proof assistant based on type theory such as
Coq~\cite{coq:refman:8.4} or Agda~\cite{norell2007towards}.  
%
However, type theory is known to be quite closed to topos theory so
one could wonder why similar techniques have not been developed in the
field of type theory. 
%
The answer to this question has been given recently by the advent of
homotopy type theory~\cite{hottbook}, which is an extension of
Martin-Löf type theory with principles inspired by (higher) category
theory and homotopy theory, such as higher inductive
types~\cite{lumsdaine2011higher,lumsdaine2013higher} and
Voevodsky's univalence principle~\cite{kapulkin2012simplicial}. 
%

@@

When restricted to mere propositions and sets, homotopy type
theory corresponds quite closely to topos theory but the mismatch
starts when considering higher homotopy types.
%
Fortunately, a higher version of topos theory has been developed
recently by mathematicians, synthesized in the monograph of Lurie on
higher topos theory~\cite{lurie}. 
%
Lurie has developed all the tools that have been defined in
topos theory, but in a higher setting. In particular, the theory of
sheaves has been lifted to higher topos theory.
%
As the notion of higher topoi appears to correspond very closely to
homotopy type theory, this provides a new hope that tackling the
problem of extending the power of homotopy type theory using
sheafification is actually possible.

Nevertheless, the adaptation of the sheafification in higher topos
theory to homotopy type theory is not straightforward because the
construction in higher topoi is restricted to the initial Grothendieck
setting which is still very topologically oriented, and not very
amenable to formalization in type theory. It seems more promising to
use a generalized notion of sheafification, called Lawvere-Tierney
sheafification~\cite{tierney1972sheaf,maclanemoerdijk}, but this construction has not
been considered yet in the setting of higher topos theory. This rises
two issues that this paper addresses: (i) how to lift the notion of
Lawvere-Tierney sheafification to higher topos theory and (ii) is it
possible to formalize this new definition in homotopy type theory.

@@

Lawvere-Tierney sheafification in a topos $\E$ is based on an abstract
point of view on the topology to be considered, being simply an
endomorphism on the classifying object $\Omega$ of $\E$  
%
$$
j : \Omega \rightarrow \Omega
$$
%
that is required to preserve $\True$ ($j \ \True = \True$), to be
idempotent ($j \circ j = j$) and compatible with products ($j \circ
\wedge = \wedge \circ (j, j)$).
%
A typical example is given by double negation.

@@

To extend Lawvere-Tierney sheafification to homotopy type theory, the
first thing to realize is that the construction can not be done in one
single step anymore. It must rather be performed by induction on the
level of homotopy types. More precisely, the first layer of
sheafification is defined for $\Type_{0}$, given a topology on
$\Type_{-1}$. This part corresponds to sheafification for topoi. Then,
assuming that the sheafification has been constructed up to level $n$,
one can defined the sheafification for $\Type_{n+1}$.
%
This inductive process in the definition of sheafification is similar
to construction in the Grothendieck setting, where the
sheafification is obtained by applying the plus-construction $n+1$
times to
$n$-types~\cite[Chapter~6]{lurie}.

@@

Compare to the definition of sheafification in topos theory, the main
change comes from the fact that in homotopy type theory, there is not
a single object classifier but rather an $n$-object classifier for
each $n\geq -2$ which classifies functions with $n$-truncated homotopy
fibers~\cite{sets_in_hott}. This means that when monomorphisms are used in topos
theoretic definition, the correct generalization may be $n$-truncated homotopy
fibers or embeddings (\ie $-1$-truncated homotopy
fibers) depending on the purpose of the definition.

@@

In other technical difficulty is the fact that sheafification in topos
theory uses the fact that epimorphisms are coequalizers of their
kernel pairs. This properties does not holds in higher topoi, but
using Giraud-Rezk-Lurie axioms of $\infty$-topoi, the same property
holds by replacing kernel pairs by \v{C}ech nerves in the statement.

Finally, one of the main difficulty in our formalization is that many
equalities which are trival (by proof irrelevance) in the topos theoretic
setting becomes relevant and requires a carreful use of univalence
with appropriate isomorphisms and a lot of reasoning on equalities
between paths.

@@

Section~\ref{sec:hott} defines the foundations of homotopy type theory
and presents a particular case of Giraud-Rezk-Lurie axioms. 
%
Section~\ref{sec:lexmod} introduces the notion of left-exact stratified
modalities, on which this paper is based.
%
Section~\ref{sec:sheaves} defines Lawvere-Tierney sheaves in homotopy
type theory.
%
Section~\ref{sec:sheafification} explains the construction of the
sheafification functor.
%
The presentation of this paper uses an informal presentation of
homotopy type theory, working entirely inside of Univalent
Foundations. 
 %
Section~\ref{sec:formalization} discusses the details of the
formalization in Coq using formal type theory, in particular issues
concerning universe polymorphism.
%
Finally, Section~\ref{sec:future-works} concludes on future works.

@@

In this section, we review some basic definitions in homotopy type
theory that are central in our formalization but not specific to
sheafification. 
%
Section~\ref{ssec:hott} introduces the notion of homotopy types and
classifying objects as defined in~\cite{sets_in_hott}.
%
Section~\ref{sec:epi-mono-fact} presents the usual epi-mono
factorization system in the light of homotopy type theory.
%
Section~\ref{sec:colim-homot-type} introduces the notion of colimits
in homotopy type theory. 
%
And Section~\ref{sec:giraud-ax} defines a particular case of
Giraud-Rezk-Lurie axioms on higher topoi that we need in the
definition of sheafification.
%
The definition of Section~\ref{ssec:hott} are part of the Coq library
available at \url{https://github.com/HoTT/HoTT}, while other definitions
and theorems are specific to our formalization.

As a prerequisite, we encourage the reader to be familiar with type theory and
in particular the point of view developed
in~\cite{hottbook}. Nevertheless, we recall most of the central definitions 
that we use so that the paper is sufficiently self-contained.
%
We note $\prod_{x:T} U$ for the dependent product, $\sum_{x:T} U$ for
the dependent sum, and $\pi_1, \pi_2$ for the first and second
projection of a dependent pair. We use informal mathematical language
instead of type theory whenever it is possible to ease the
reading, without making our statement imprecise. In particular,
(higher) inductive types are defined using itemization to avoid an
overhead of notation.

@@

As noticed in \cite{hottbook}, left exact modalities corresponds 
to sub-$(\infty,1)$-topoi. Indeed, modal types defines a new type
theory as modality preserves all type former, such as dependent
products or dependent sums.
% or inductive types (\nt{double check that}).

@@

The definition of a dense $n$-subobject requires more work as the
characteristic function $\chi_E$ of $E$ seen as an $n$-subobject of
itself is not the constant function equal to $\one$, as it is the case
for topoi, but rather the map 
%
$$\chi_E  = \lambda e . \ \sum_{e':E} e=e'.$$
%
This means that we need to take more care of the homotopy structure of
this charactestic function, and in particular, the definition of a
dense $n$-subobject comes with an additional coherence condition
(which is trivial when $n=-1$).

@@

Note that these definitions are almost the same as the ones
in~\cite{maclanemoerdijk}. The main difference is that {separated}
is defined for $n$-subobjects, while {sheaf} only for
$(-1)$-subobjects.
%
For higher topos theory, in the Grotehndieck setting, sheaves seems
to correspond to the second part of our definition only (assuming that
Lawvere-Tierney topologies can still be shown to subsume Grothendieck
toplogies for $(\infty,1)$-topoi, which is beyond the scope of this paper).
%

A fundamental property in the construction of the sheafification
functor is the fact that the type of modal types at level $n$ defines
a sheaf.
%
This property initially holds in the topos theoretic construction, but
it requires much work here, as we have to deal with equalities. In
particular, this property uses the specific definition
of separated types and sheaves, which shows that we had actually no
choice in their statement.

@@

Let $T : \Type_{n+1}$. We define $\separated T$ as the image (see
Section~\ref{sec:epi-mono-fact}) of
$\modal_n^T \circ \{\cdot\}_T$, as in
$$\xymatrix{
  T \ar[r]^{\{\cdot\}_T} \ar[d]_{\mu_T} & \Type_n^T \ar[d]^{\modal_n^T} \\
  \separated T \ar[r]& \left( \Type_n^\modal \right)^T
}, $$
where $\{\cdot\}_T$ is the singleton map $\lambda (t:T),~\lambda
(t':T),~t=t'$.
%
$\separated T$ can be given explicitly by
%
$$
\begin{array}{rcl}
\separated T &\defeq & \im (\lambda~t:T,~\lambda~ t',~ \modal_n (t = t')) \\
          & \defeq & \sum_{u:T \to \Type_n^\modal} \left\| \sum_{a:T} 
            (\lambda t,~\modal_n (a=t)) = u\right\|.
\end{array}
$$
%
This corresponds to the free separated object used in the topos
theoretic construction, but using $\Type_n^\modal$ instead of the
$j$-subobject classifier $\Omega_j$.
%
\begin{prop}
  For any $T:\Type_{n+1}$, $\separated T$ is separated.  
\end{prop}

@@

Overall, with other files containing technical lemmas, the project
contains 6322 lines, and it could be reduced a bit by improving the
way Coq tries to rewrite and apply lemmas automatically. 
The \texttt{coqwc} tool counts 2000 lines of specifications
(definitions, lemmas, theorems, propositions) and 3700 lines of proof
script.
%
This constitutes a significant amount of work but the part dedicated
to sheaves and sheafification is only 2200 lines of proof script,
which seems quite reasonable and encouraging, because it suggests
that homotopy type theory provides a convenient tool to formalize some
part of the theory of higher topoi. As a matter of comparison, this
\TeX\xspace file contains approximatively 1800 lines.

@@

As a future work, we would like to improve this construction in two
ways:
\begin{itemize}
\item 
  At the moment, sheafification only works with truncated
  types. This is fine from a programming point of view, 
  but many important types in homotopy theory are not
  truncated, \eg the circle $\mathbb S^1$.  Thus, we plan to extend
  the sheafification to all types by using a
  limit construction.
\item 
  In this work, a particular case of a Giraud-Rezk-Lurie axiom has
  been admitted. The work done in~\cite[Chapter 6]{lurie} suggests,
  considering that homotopy type theory is a language for higher topos
  theory, that this axiom is provable. We plan to investigate whether the
  higher topos theoretic proof can be adapted to our setting.
  %
  % A computer-checked proof of this fact would improve our
  % developpement.
\end{itemize}
Moreover, in topos theory, Lawvere-Tierney subsumes Grothendieck~\cite[Section~V.4]{maclanemoerdijk} in the sense that any
Grothendieck topology gives rise to a Lawvere-Tierney topology with
the same notion of sheaves. Higher Lawvere-Tierney sheaves are
presented here, and higher Grothendieck sheaves have been defined
in~\cite{lurie}. It should be interesting to check if the subsumption
remains true in higher topos theory.

>>>>

  Sheafification is a popular tool in topos theory which
  allows to extend the internal logic of a topos with new
  principles. One of its most famous applications is the possibility
  to transform a topos into a boolean topos using the
  dense topology, which corresponds in essence to Gödel's double
  negation translation.
  % 
  The same construction has not been developed in Martin-Löf type
  theory because of a mismatch between topos theory and type theory. This
  mismatched has been fixed recently by considering homotopy type
  theory, an extension of Martin-Löf type theory with new
  principles inspired by category theory and homotopy theory, and
  which corresponds closely to higher toposes.
  % 
  In this paper, we give a computer-checked construction of
  Lawvere-Tierney sheafification in homotopy type theory, which allows
  in particular to give a meaning to the (propositional) law of
  excluded middle inside homotopy type theory, being
  compatible with the full type-theoretic axiom of choice.

@@

Sheafification~\cite{maclanemoerdijk} is a very powerful geometric
construction that has been initially stated in topology and has
quickly been lifted to mathematical logic.
%
In the field of topos theory, it provides a way to construct new toposes
from already existing ones, allowing logical principles---that can not
be proven to be true or false in the old topos---to be valid (or
invalid) in the new topos.
%
The most common use of sheafification is the construction a boolean
topos, thus validating the classical principle of the law of excluded
middle (EM), from an intuitionistic topos using the dense topology. 
%
An other famous application has been developed by
Cohen~\cite{cohen1966} to prove that the continuum hypothesis is
independent of the usual axioms of Zermelo-Fr\ae nkel set theory, even
in presence of the axiom of choice (AC). The initial work of Cohen
uses forcing but can be rephrased in terms of
sheafification~\cite{maclanemoerdijk}.

@@

Unfortunately, all those works---although they provide very nice and
sophisticated theoretical results---do not share the generality and
simplicity of sheafification in topos theory and are not amenable to a
direct integration into a proof assistant based on type theory such as
Coq~\cite{coq:refman:8.4} or Agda~\cite{norell2007towards}.  
%
However, type theory is known to be quite closed to topos theory so
one could wonder why similar techniques have not been developed in the
field of type theory. 
%
The answer to this question has been given recently by the advent of
homotopy type theory~\cite{hottbook}, which is an extension of
Martin-Löf type theory with principles inspired by (higher) category
theory and homotopy theory, such as higher inductive
types~\cite{lumsdaine2011higher,lumsdaine2013higher} and
Voevodsky's univalence principle~\cite{kapulkin2012simplicial}. 
%

@@

When restricted to mere propositions and sets, homotopy type
theory corresponds quite closely to topos theory but the mismatch
starts when considering higher homotopy types.
%
Fortunately, a higher version of topos theory has been developed
recently by mathematicians, synthesized in the monograph of Lurie on
higher topos theory~\cite{lurie}. 
%
Lurie has presented all the tools that have been defined in
topos theory, but in a higher setting. In particular, the theory of
sheaves has been lifted to higher topos theory.
%
As the notion of higher toposes appears to correspond very closely to
homotopy type theory, this provides a new hope that tackling the
problem of extending the power of homotopy type theory using
sheafification is actually possible.

Nevertheless, the adaptation of the sheafification in higher topos
theory to homotopy type theory is not straightforward because the
construction in higher toposes is restricted to the initial Grothendieck
setting which is still very topologically oriented, and not very
amenable to formalization in type theory. It seems more promising to
use a generalized notion of sheafification, called Lawvere-Tierney
sheafification~\cite{tierney1972sheaf,maclanemoerdijk}, but this construction has not
been considered yet in the setting of higher topos theory. This rises
two issues that this paper addresses: (i) how to lift the notion of
Lawvere-Tierney sheafification to higher topos theory and (ii) is it
possible to formalize this new definition in homotopy type theory.

@@

Lawvere-Tierney sheafification in a topos $\E$ is based on an abstract
point of view on the topology to be considered, being simply defined by an
endomorphism on the classifying object $\Omega$ of $\E$  
%
$$
j : \Omega \rightarrow \Omega
$$
%
that is required to preserve $\True$ ($j \ \True = \True$), to be
idempotent ($j \circ j = j$) and compatible with products ($j \circ
\wedge = \wedge \circ (j, j)$).
%
A typical example is given by double negation.

@@

To extend Lawvere-Tierney sheafification to homotopy type theory, the
first thing to understand is that the construction can not be done in one
single step anymore. It must rather be performed by induction on the
level of homotopy types. More precisely, the first layer of
sheafification is defined for $\Type_{0}$, given a topology on
$\Type_{-1}$. This part corresponds to sheafification for toposes. Then,
assuming that the sheafification has been constructed up to level $n$,
one can defined the sheafification for $\Type_{n+1}$.
%
This inductive process in the definition of sheafification is similar
to construction in the Grothendieck setting, where the
sheafification is obtained by applying the plus-construction $n+1$
times to
$n$-types~\cite[Chapter~6]{lurie}.

@@

Compare to the definition of sheafification in topos theory, the main
change comes from the fact that in homotopy type theory, there is not
a single object classifier but rather an $n$-object classifier for
each $n\geq -2$ which classifies functions with $n$-truncated homotopy
fibers~\cite{sets_in_hott}. This means that when monomorphisms are used in topos-theoretic definition, the correct generalization may be $n$-truncated homotopy
fibers or embeddings (\ie $-1$-truncated homotopy
fibers) depending on the purpose of the definition.

@@

Another technical difficulty is the fact that sheafification in topos
theory uses the property that epimorphisms are coequalizers of their
kernel pairs. This properties does not hold anymore in higher toposes, but
using Giraud-Rezk-Lurie axioms of $\infty$-toposes, the same property
holds by replacing kernel pairs by \v{C}ech nerves in the statement.

Finally, one of the main difficulty in our formalization is that many
equalities which are trival (by proof irrelevance) in the topos-theoretic
setting becomes relevant and requires a carreful use of univalence
with appropriate isomorphisms and a lot of reasoning on equalities
between paths.

@@

Section~\ref{sec:hott} presents the foundations of homotopy type theory
and defines a particular case of Giraud-Rezk-Lurie axioms. 
%
Section~\ref{sec:lexmod} introduces the notion of left-exact stratified
modalities, on which this paper is based.
%
Section~\ref{sec:sheaves} defines Lawvere-Tierney sheaves in homotopy
type theory.
%
Section~\ref{sec:sheafification} explains the construction of the
sheafification functor.
%
The definitions of this paper uses an informal presentation of
homotopy type theory, working entirely inside of Univalent
Foundations. 
 %
Section~\ref{sec:formalization} discusses the details of the
formalization in Coq using formal type theory, in particular issues
concerning universe polymorphism.
%
Finally, Section~\ref{sec:future-works} concludes on future works.

@@

In this section, we review some basic definitions in homotopy type
theory that are central in our formalization but not specific to
sheafification. 
%
Section~\ref{ssec:hott} introduces the notion of homotopy types and
classifying objects as defined in~\cite{sets_in_hott}.
%
Section~\ref{sec:epi-mono-fact} presents the usual epi-mono
factorization system in the light of homotopy type theory.
%
Section~\ref{sec:colim-homot-type} introduces the notion of colimits
in homotopy type theory. 
%
And Section~\ref{sec:giraud-ax} defines a particular case of
Giraud-Rezk-Lurie axioms on higher toposes that we need in the
definition of sheafification.
%
The definition of Section~\ref{ssec:hott} and \ref{sec:epi-mono-fact}
are part of the Coq library
available at \url{https://github.com/HoTT/HoTT}, while other definitions
and theorems are specific to our formalization.

As a prerequisite, we encourage the reader to be familiar with type theory and
in particular the point of view developed
in~\cite{hottbook}. Nevertheless, we recall most of the central definitions 
that we use so that the paper is sufficiently self-contained.
%
We note $\prod_{x:T} U$ for dependent products, $\sum_{x:T} U$ for
dependent sums, and $\pi_1, \pi_2$ for the first and second
projection of a dependent pair. We use informal mathematical language
instead of type theory whenever it is possible, to ease the
reading without making our statement imprecise. In particular,
(higher) inductive types are defined using itemization to avoid an
overhead of notation.

@@

As noticed in \cite{hottbook}, left exact modalities corresponds 
to sub-$(\infty,1)$-toposes. Indeed, modal types defines a new type
theory as modality preserves all type former, such as dependent
products or dependent sums.
% or inductive types (\nt{double check that}).

@@

The definition of a dense $n$-subobject requires more work as the
characteristic function $\chi_E$ of $E$ seen as an $n$-subobject of
itself is not the constant function equal to $\one$, as it is the case
for toposes, but rather the map 
%
$$\chi_E  = \lambda e . \ \sum_{e':E} e=e'.$$
%
This means that we need to take more care of the homotopy structure of
this charactestic function, and in particular, the definition of a
dense $n$-subobject comes with an additional coherence condition
(which is trivial when $n=-1$).

@@

Note that these definitions are almost the same as the ones
in~\cite{maclanemoerdijk}. The main difference is that {separated}
is defined for $n$-subobjects, while {sheaf} only for
$(-1)$-subobjects.
%
For higher topos theory, in the Grotehndieck setting, sheaves seems
to correspond to the second part of our definition only (assuming that
Lawvere-Tierney topologies can still be shown to subsume Grothendieck
toplogies for $(\infty,1)$-toposes, which is beyond the scope of this paper).
%

A fundamental property in the construction of the sheafification
functor is the fact that the type of modal types at level $n$ defines
a sheaf.
%
This property initially holds in the topos-theoretic construction, but
it requires much work here, as we have to deal with equalities. In
particular, this property uses the specific definition
of separated types and sheaves, which shows that we had actually no
choice in their statement.

@@

Let $T : \Type_{n+1}$. We define $\separated T$ as the image (see
Section~\ref{sec:epi-mono-fact}) of
$\modal_n^T \circ \{\cdot\}_T$, as in
$$\xymatrix{
  T \ar[r]^{\{\cdot\}_T} \ar[d]_{\mu_T} & \Type_n^T \ar[d]^{\modal_n^T} \\
  \separated T \ar[r]& \left( \Type_n^\modal \right)^T
}, $$
where $\{\cdot\}_T$ is the singleton map $\lambda (t:T),~\lambda
(t':T),~t=t'$.
%
$\separated T$ can be given explicitly by
%
$$
\begin{array}{rcl}
\separated T &\defeq & \im (\lambda~t:T,~\lambda~ t',~ \modal_n (t = t')) \\
          & \defeq & \sum_{u:T \to \Type_n^\modal} \left\| \sum_{a:T} 
            (\lambda t,~\modal_n (a=t)) = u\right\|.
\end{array}
$$
%
This corresponds to the free separated object used in the topos-theoretic construction, but using $\Type_n^\modal$ instead of the
$j$-subobject classifier $\Omega_j$.
%
\begin{prop}
  For any $T:\Type_{n+1}$, $\separated T$ is separated.  
\end{prop}

@@

Overall, with other files containing technical lemmas, the project
contains 6322 lines, and it could be reduced a bit by improving the
way Coq tries to rewrite and apply lemmas automatically. 
The \texttt{coqwc} tool counts 2000 lines of specifications
(definitions, lemmas, theorems, propositions) and 3700 lines of proof
script.
%
This constitutes a significant amount of work but the part dedicated
to sheaves and sheafification is only 2200 lines of proof script,
which seems quite reasonable and encouraging, because it suggests
that homotopy type theory provides a convenient tool to formalize some
part of the theory of higher toposes. As a matter of comparison, this
\TeX\xspace file contains approximatively 1800 lines.

@@

As a future work, we would like to improve this construction in two
ways:
\begin{itemize}
\item 
  At the moment, sheafification only works with truncated
  types. This is fine from a programming point of view, 
  but many important types in homotopy theory are not
  truncated, \eg the circle $\mathbb S^1$.  Thus, we plan to extend
  the sheafification to all types by using a
  limit construction.
\item 
  In this work, a particular case of a Giraud-Rezk-Lurie axiom has
  been admitted. The work done in~\cite[Chapter 6]{lurie} suggests,
  considering that homotopy type theory is a language for higher topos
  theory, that this axiom is provable. We plan to investigate whether the
  higher-topos-theoretic proof can be adapted to our setting.
  %
  % A computer-checked proof of this fact would improve our
  % developpement.
\end{itemize}
Moreover, in topos theory, Lawvere-Tierney subsumes Grothendieck~\cite[Section~V.4]{maclanemoerdijk} in the sense that any
Grothendieck topology gives rise to a Lawvere-Tierney topology with
the same notion of sheaves. Higher Lawvere-Tierney sheaves are
presented here, and higher Grothendieck sheaves have been defined
in~\cite{lurie}. It should be interesting to check if the subsumption
remains true in higher topos theory.
